%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{xcolor}
\usepackage{fontawesome}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithYear}[3][ ]{ % First argument is optional
  \item\small{
    #2 \hfill {\small #3} \\
    #1
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% Custom command for formatting publication subheadings
\newcommand{\resumePublicationHeading}[1]{
  \vspace{5pt} % Adjust space before the heading if needed
  \noindent\textbf{\small #1} % Apply small font size and bold to the heading
  \vspace{2pt} % Adjust space after the heading if needed
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \text{\Huge \scshape Emory Richardson} \\ \vspace{1pt}
    \textit{\scshape Data Scientist $\cdot$} \\ \vspace{1pt}
    \small 
    \faEnvelope\ rchrdsn.emory -at- gmail.com $|$ 
    \faHome\ \href{https://github.com/rchrdsnemory}{rchrdsnemory.github.io} $|$
    %\faLinkedin\ \href{https://linkedin.com/in/...}{linkedin.com/in/emory-richardson/} $|$ 
    \faGithub\ \href{https://github.com/rchrdsnemory}{github.com/rchrdsnemory}
\end{center}



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {École Normale Supérieure (ENS-PSL), Institut Jean Nicod}{\textit{Expected graduation}: September 2025}
      {PhD Psychology}{Paris, France}
            \resumeItemListStart
        \resumeItem{Supervisors: Hugo Mercier \& Kevin Arceneaux}
        \resumeItem{Thesis: Essays on Understanding Trust in Science}
      \resumeItemListEnd
    \resumeSubheading
      {École Normale Supérieure (ENS-PSL)}{2020 -- 2022}
      {MA Cognitive Science}{Paris, France}
            \resumeItemListStart
        \resumeItem{Supervisor: Hugo Mercier}            
        \resumeItem{Thesis: Can we infer people are accurate and competent merely because they agree with each other?}
      \resumeItemListEnd
    \resumeSubheading
      {Universität Freiburg}{2019 -- 2020}
      {MA Journalism, 1st year}{Freiburg, Germany} 
    \resumeSubheading
      {Universität Konstanz}{2014 -- 2018}
      {BA Political Science and Public Administration}{Konstanz, Germany}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Direction Interministérielle de la Transformation Publique (DITP)}{June 2021 -- August 2021}
      {Research Intern}{Paris, France}
      
    \resumeSubheading
      {Assemblée Nationale}{September 2018 -- July 2019}
      {Parliamentary Assistant}{Paris, France}

    \resumeSubheading
      {University of St. Gallen}{June 2017 -- July 2018}
      {Research Assistant}{St. Gallen, Switzerland}
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}


% Set font size for the entire Publications section
\small

\noindent\textcolor{gray}{\textit{\footnotemark[1]first author}}
\vspace{5pt} % Adjust the space if needed

% Use custom command for subheadings
\resumePublicationHeading{Peer Reviewed Publications}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in]
    \resumeItem{\textbf{Pfänder, J.\footnotemark[1]}, \& Altay, S. (2025). Spotting false news and doubting true news: A systematic review and meta-analysis of news judgements. \emph{Nature Human Behaviour}. \url{https://doi.org/10.1038/s41562-024-02086-1}
    }
    \resumeItem{\textbf{Pfänder, J.\footnotemark[1]}, de Courson, B., & Mercier, H. (2025). How wise is the crowd: Can we infer people are accurate and competent merely because they agree with each other? \emph{Cognition, 255, 106005}. \url{https://doi.org/10.1016/j.cognition.2024.106005}
    }

    % Add more published publications as needed
\end{enumerate}

\resumePublicationHeading{Conference Proceedings}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in, resume]
    \resumeItem{\textbf{Pfänder, J.\footnotemark[1]}, de Courson, B., & Mercier, H. (2024). How wise is the crowd: Can we infer people are accurate and competent merely because they agree with each other? \emph{Proceedings of the Annual Meeting of the Cognitive Science Society, 46(0)}. \url{https://escholarship.org/uc/item/4ms2n8wd}
    }

\end{enumerate}

\resumePublicationHeading{Large collaborations}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in, resume]
    \resumeItem{Cologna, V., Mede, N. G., Berger, S., Besley, J., Brick, C., Joubert, M., Maibach, E., Mihelj, S., Oreskes, N., Schäfer, M. S., & Linden, D. S. van der., ..., Mercier, H., ..., \textbf{Pfänder, J.}, ... et al. (2024). Trust in scientists and their role in society across 67 countries. \emph{Nature Human Behaviour}. \url{https://doi.org/10.1038/s41562-024-02090-5}
    }
    
    \resumeItem{Mede, N. G., Cologna, V., Berger, S., Besley, J., Brick, C., Joubert, M., Maibach, E., Mihelj, S., Oreskes, N., Schäfer, M. S., & Linden, D. S. van der., ..., Mercier, H., ..., \textbf{Pfänder, J.}, ... et al. (2024). Perceptions of Science, Science Communication, and Climate Change Attitudes in 67 Countries: The TISP Dataset. \emph{Scientific Data}. \url{https://doi.org/10.1038/s41597-024-04100-7} 
    }

\end{enumerate}

\resumePublicationHeading{Working Papers}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in, resume]
    \resumeItem{\textbf{Pfänder, J.\footnotemark[1]}, Kerzreho, L. & Mercier, H. (2024). Quasi-universal acceptance of basic science in the US. \url{https://doi.org/10.31219/osf.io/qc43v} \emph{(Under review)}
    }
    \resumeItem{\textbf{Pfänder, J.\footnotemark[1]}, Rouilhan, S. D., & Mercier, H. (2025). Trusting but forgetting impressive science. \url{https://doi.org/10.31219/osf.io/argq5_v1} \emph{(Under review)}
    }
    \resumeItem{\textbf{Pfänder, J.\footnotemark[1]}, & Mercier, H. (2025). The French trust more the sciences they perceive as precise and consensual. \url{https://doi.org/10.31219/osf.io/k9m6e_v1} \emph{(Under review)}
    }    

\end{enumerate}


%-----------Presentations-----------
\section{Presentations}

\resumePublicationHeading{Conferences}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in]
    \resumeItemWithYear{\textbf{Spotting False News and Doubting True News. A Meta-Analysis of News Judgments  (Keynote)}}{2025}{\textit{Infox sur Seine, Paris}}    
        \resumeItemWithYear{\textbf{How wise is the crowd -- Can we infer people are accurate and competent \\ merely because they agree with each other? (Poster)}}{2024}{\textit{46th Annual Meeting of the Cognitive Science Society, Rotterdam}}
    \resumeItemWithYear{\textbf{Processus sous-tendant la confiance dans la science}}{2024}{\textit{5ème édition des Rencontres Jeunes Chercheur·euse·s, Grenoble}}
    \resumeItemWithYear{\textbf{Spotting False News and Doubting True News: A Meta-Analysis of News Judgments}}{2024}{\textit{EDMO Scientific Conference on Disinformation, Amsterdam}}
\end{enumerate}



\resumePublicationHeading{Invited talks}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in, resume]
    \resumeItemWithYear{\textbf{Trust in science}}{2025}{\textit{Paris School of International Affairs, Paris}
\end{enumerate}

%-----------Teaching-----------
\section{Teaching}

% Intermediate heading for Courses
\subsection*{Courses}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Fact-Checking and Critical Thinking} $|$ \emph{Université PSL (Paris Sciences \& Lettres)}}{2022 -- Present}
          \resumeItemListStart
            \resumeItem{A hands-on introduction to research design for the interdisciplinary BA program \\ "Sciences pour un monde durable"}
            \resumeItem{Sole instructor \& creator of the course}
            \resumeItem{30h in-class per semester; one semester a year}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

% Intermediate heading for Courses
\subsection*{Workshops}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Meta-analysis for beginners}}{}
          \resumeItemListStart
          \resumeItemWithYear{Laboratoire de Psychologie du Développement et  de l'Éducation de l'Enfant (LaPsyDÉ)}{2024}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

% Intermediate heading for Courses
\subsection*{Student internship supervision}
% for subheadings, use:
% \resumePublicationHeading{E.g. Master students}
\begin{enumerate}[label={[{\arabic*.}]}, left=0.15in]
    \resumeItemWithYear{Mateo Pivert, \textit{undergraduate}}{2024}
    \resumeItemWithYear{Ludivine Million, \textit{undergraduate}}{2024}
    \resumeItemWithYear{Prune Lefevre Jachimowicz, \textit{undergraduate}}{2024}
    \resumeItemWithYear{Lou Kerzreho, \textit{graduate}}{2023}
    \resumeItemWithYear{Kevin Chen, \textit{undergraduate}}{2023}
    \resumeItemWithYear{Théodore Lellouche, \textit{undergraduate}}{2022}
\end{enumerate}

%-----------Other-----------
\section{Professional Service}
\resumeSubHeadingListStart

\resumeSubheading
  {(Supervised) Ad-hoc reviewer for}{}  
  {\parbox[t]{0.9\textwidth}{Nature Climate Change (1), Public Understanding of Science (1), PNAS Nexus (1), Social Science \& Medicine (1), Društvena istraživanja (Croatian social science review) (1)}}{}

\resumeSubHeadingListEnd

\section{External Coursework \& Summer Schools}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Diverse Intelligences Summer Institute}{July 2024}
      {Hosted by the University of St. Andrews and organized by Indiana University Bloomington
}{St. Andrews, UK}

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: German, English, French, Spanish} \\
     \textbf{Programming}{: R, Git (basics), Python (rudimentary)} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
